---
title: "Load and Save SMM Dataset"
author: "Robert Chen"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

# Preliminaries

```{r setup, include=FALSE}

library(knitr); library(rmdformats)

opts_chunk$set(echo=TRUE,
               cache=FALSE,
               prompt=FALSE,
               tidy=FALSE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)

```

  
## Resources
  The following resources will be very helpful:\
* [RMarkdown Tutorial](https://ourcodingclub.github.io/tutorials/rmarkdown/)
* [ICD-10 codes in R](https://www.r-bloggers.com/2019/05/whats-that-disease-called-overview-of-icd-package/)
* [Parallelization in R](https://nceas.github.io/oss-lessons/parallel-computing-in-r/parallel-computing-in-r.html)
* [Future: a tutorial on parallelization in R using the futures framework](https://cran.r-project.org/web/packages/future/vignettes/future-1-overview.html)
* [Sparse matrices in R using the Matrix library](https://slowkow.com/notes/sparse-matrix/)
* [Analyzing survey data in R](https://stats.oarc.ucla.edu/r/seminars/survey-data-analysis-with-r/)
* [Using svyglm instead of lme4 for linear modeling](https://stats.stackexchange.com/questions/89204/fitting-multilevel-models-to-complex-survey-data-in-r)
* [Generalized linear models on survey data](https://stats.oarc.ucla.edu/r/faq/how-can-i-do-regression-estimation-with-survey-data/)
* [Using the srvyr package to add tidyverse to surveys](https://cran.r-project.org/web/packages/srvyr/vignettes/srvyr-vs-survey.html)
* [Textbook on complex survey designs in R](http://r-survey.r-forge.r-project.org/svybook/)

## Loading packages

First, we need to load packages that are useful for the analysis of HCUP NIS data.\
We will be primarily data wrangling using the `tidyverse` suite of packages.\
We will be using `rmarkdown` as our primary method of notebooking.\
We will also be using the package `survey` to deal with the sampling design of the NIS.\
Finally, we will be loading a series of statistical packages for complex-design analyses\


```{r load_packages, warning = FALSE, message = FALSE}

# suppressPackageStartupMessages(library(rmarkdown))
# suppressPackageStartupMessages(library(survey))
# suppressPackageStartupMessages(library(yarrr))
# suppressPackageStartupMessages(library(lme4))
# suppressPackageStartupMessages(library(lmerTest))
# suppressPackageStartupMessages(library(icd))
# suppressPackageStartupMessages(library(Matrix))
# suppressPackageStartupMessages(library(future))
# suppressPackageStartupMessages(library(future.apply))
# suppressPackageStartupMessages(library(parallel))
# suppressPackageStartupMessages(library(srvyr))
# suppressPackageStartupMessages(library(missForest))
# suppressPackageStartupMessages(library(tidyverse))

library(here); library(yarrr); library(survey)
library(lme4); library(lmerTest); library(icd)
library(Matrix); library(future); library(future.apply)
library(parallel); library(srvyr); library(tidyverse)


```

# Load and merge data

We will now load the HCUP NIS dataset from 2019 just to understand features of the dataset.\
Although we have data from 2016-2019, loading one year's worth of data will reduce memory requirements.\
Each year has several useful files worth nothing:\
* Core file: Main file containing main features including age, payer, discharge status, ICD-10 code, total charges.\
* Severity file: Additional data identifying the severity of a condition for a specific discharge.\
* Diagnosis and procedure groups file: Additional file describing ICD-10 comorbidity information and procedures.\
* Hospital file: Contains information about hospital data.\

```{r load_merge}
###### 1. Loading data from the HCUP NIS
### i. Set up a working data directory

data_dir <- "data"

### ii. Load data files for 2019
core_2019 <- read.csv(here(data_dir, "NIS_2019_Core.csv"))
hospital_2019 <- read.csv(here(data_dir, "NIS_2019_Hospital.csv"))
severity_2019 <- read.csv(here(data_dir, "NIS_2019_Severity.csv"))
cc_2019 <- read.csv(here(data_dir, "cc2019NIS.csv"))
dx_pr_grps_2019 <- read.csv(here(data_dir, "NIS_2019_DX_PR_GRPS.csv"))

### iii. Merge dx_pr_grps_2019 with core_2019
all.equal(dx_pr_grps_2019$key_nis, core_2019$key_nis)
all.equal(severity_2019$key_nis, core_2019$key_nis)
core_2019 <- cbind(core_2019, dx_pr_grps_2019[, 4:ncol(dx_pr_grps_2019)], severity_2019[, 3:ncol(severity_2019)])
core_2019 <- as.data.frame(core_2019)

###### 2. Importing files to filter for severe maternal morbidity
smm_dx_cdc <- read.table(here(data_dir, "220119_smm_dx_cdc.txt"), sep = "")
smm_pcs <- read.table(here(data_dir, "smm_pcs.txt"), sep = "")
pcs_transfusion <- read.table(here(data_dir, "220119_pcs_transfusion.txt"), sep = "")

###### 3. Importing variables that we care about
# variables_complete <- read.table(here(data_dir, "all_variables_of_interest.txt"), sep = "")
variables_core <- read.table(here(data_dir, "core_variables_of_interest.txt"), sep = "") %>% unlist

### i. Clean up core variables
names(variables_core) <- NULL
### ii. Extract cmr variable names
other_columns <- colnames(core_2019)[grepl('^cmr_', colnames(core_2019))]
### iii. Append
variables_core <- c(variables_core, other_columns, c("aprdrg_risk_mortality", "aprdrg_severity"))

```

## Creating a delivery dataset

```{r delivery_filter}
###### 1. Subsetting the data to only deliveries
core_2019_subset <- core_2019[, variables_core]
deliv_2019 <- subset(core_2019_subset, i10_delivery == 1)


###### 2. Add hospital data columns
match1 <- hospital_2019[match(deliv_2019$hosp_nis, hospital_2019$hosp_nis), c(5,2,3,4,6,7,9,10,11,12,13)]
all.equal(deliv_2019$hosp_nis, match1$hosp_nis) # TRUE
match1$hosp_nis <- NULL
deliv_2019 <- cbind(deliv_2019, match1)
remove(match1)

###### 3. Add cost-to-charge ratios
match1 <- cc_2019[match(deliv_2019$hosp_nis, cc_2019$hosp_nis), c(1,3,4)]
all.equal(deliv_2019$hosp_nis, match1$hosp_nis) # TRUE
match1$hosp_nis <- NULL
deliv_2019 <- cbind(deliv_2019, match1)
remove(match1)

###### 4. Check the percentage of missing datapoints there are
apply(deliv_2019, 2, function(x){sum(is.na(x))/length(x)}) %>% unlist()

###### 5. Mutate columns that need to be factors
apply(deliv_2019, 2, function(x){is.numeric(x)})
### i. Update all factors
non_factors <- c('age', 'discwt', 'i10_ndx', 'i10_npr', 'los', 'totchg', 'n_disc_u', 'n_hosp_u', 's_disc_u', 's_hosp_u', 'total_disc', 'ccr_nis', 'wageindex')
for(i in 1:ncol(deliv_2019)){
  current_colname <- colnames(deliv_2019[i])
  if(current_colname %in% non_factors){
    next
  } else{
    deliv_2019[, current_colname] <- as.factor(deliv_2019[, current_colname])
  }
}

# ###### 6. Create a survey design for deliveries
# svy_deliv <- svydesign(id = ~hosp_nis,
#                        strata = ~nis_stratum,
#                        weights = ~discwt,
#                        nest = TRUE,
#                        survey.lonely.psu = "adjust",
#                        data = deliv_2019)
```

## Creating a SMM dataset

SMM is defined as any delivery that has a medical diagnosis code of SMM, has a transfusion procedure code, or a procedure code associated with SMM excluding transfusions.\
These are nicely summarized in three files that Clara Kao put together.

```{r smm_filter}
###### 1. Creating a smaller dataset of icd codes only
### i. Subset a dataset that only has icd codes and procedure codes
deliv_icd <- subset(core_2019, i10_delivery == 1)
deliv_icd <- deliv_icd[, grepl('^i10_dx|i10_pr', colnames(deliv_icd))]
### ii. Identify the unique icd codes
unique_codes <- unique(
  unlist(
    apply(deliv_icd, 2, function(x){
    temp <- unique(x)
    temp <- temp[temp != ""]
    }
    )
  )
)
length(unique_codes) # 10614 unique ICD or procedure codes
### iii. Set up the universe of codes to search against
smm_related_codes <- c(unlist(smm_dx_cdc), unlist(smm_pcs), unlist(pcs_transfusion))
names(smm_related_codes) <- NULL
# Set up multisession parameters to 'parallelize' in RStudio
plan(multisession, workers = availableCores(), gc = TRUE)
options(future.globals.maxSize = 16000 * 1024 ^ 2)
# Use future_lapply to go through and create a TRUE/FALSE boolean list matching to each row and whether the icd or procedure codes appear in the universe of SMM-defined codes

temp1 <- future.apply::future_lapply(1:nrow(deliv_icd), function(x){
  current_icd_codes <- unlist(deliv_icd[x, ])
  current_icd_codes <- current_icd_codes[current_icd_codes != ""]
  if(length(current_icd_codes) == 0){
    break
  } else{
    sum(current_icd_codes %in% smm_related_codes) > 0
  }
}) 

temp1 <- unlist(temp1) 

###### 2. Creating an SMM-specific dataset
### i. Exclude NAs or any transfers in or out of the hospital during admission
smm_2019 <- subset(deliv_2019, temp1)
smm_2019 <- subset(smm_2019, !is.na(tran_in))
smm_2019 <- subset(smm_2019, tran_in == 0)
smm_2019 <- subset(smm_2019, !is.na(tran_out))
smm_2019 <- subset(smm_2019, tran_out == 0)

smm_2019 <- smm_2019 %>% select(-c("hosp_division.1")) # quick fix to a duplicated column

saveRDS(smm_2019, here(data_dir, "regression_data_smm_nonimputed.rds"))
```
